%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%-----------HEADING-----------
\begin{center}
    \textbf{\Huge \scshape Basil Reji} \\ \vspace{1pt}
    \small +91 8921307045 $|$
    \href{mailto:rejibasilp@gmail.com}{\underline{rejibasilp@gmail.com}} $|$
    \href{https://github.com/capdevbasil}{\underline{github.com/capdevbasil}} $|$
    \small Remote (Kerala, India)
\end{center}

%-----------SUMMARY-----------
\small{Full-Stack Developer with 6 years of experience specializing in React, Next.js, NestJS, and AWS. Proven track record of owning the entire stack — from database design to cloud deployment — for systems supporting 50K+ users with 99.9\% uptime, across real estate, fleet management, and service platforms.}

\vspace{4pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Fullstack Developer (Remote)}{May 2025 -- Present}
      {Summitcode Experts}{Sharjah, UAE}
      \resumeItemListStart
        \resumeItem{Sole engineer responsible for architecting and shipping a full service booking management platform (Motorhub) using Next.js, Node.js, AWS, and PostgreSQL — delivered 100\% on time.}
        \resumeItem{Built and managed the complete stack independently: UI, REST API, AWS infrastructure, and CI/CD pipeline.}
        \resumeItem{Implemented secure authentication using AWS Cognito and optimized data fetching with SWR caching.}
        \resumeItem{Improved sprint predictability through Scrum practices, reducing carry-over by 20\% and raising team velocity.}
        \resumeItem{Led code reviews that reduced production bugs by 10\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior React Developer}{Nov 2024 -- May 2025}
      {Zora Technologies}{Trivandrum, Kerala}
      \resumeItemListStart
        \resumeItem{Built a fleet management web application using React, Mantine UI, and Clerk authentication, with SWR for API caching.}
        \resumeItem{Mentored junior developers through structured knowledge-sharing, improving team productivity by 30\%.}
        \resumeItem{Set up CI/CD pipelines using Azure DevOps, increasing deployment frequency by 20\%.}
        \resumeItem{Ensured fully responsive, device-optimized UI across all screen sizes.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Engineer $\rightarrow$ Senior Engineer}{Jul 2020 -- Nov 2024}
      {dbiz.ai}{Kochi, Kerala}
      \resumeItemListStart
        \resumeItem{Scaled REST APIs built with NestJS and PostgreSQL to serve 50,000+ monthly active users at 99.9\% uptime.}
        \resumeItem{Cut global search API latency from 800ms to 45ms by integrating Elasticsearch with real-time search-as-you-type indexing.}
        \resumeItem{Integrated backend services with Sitecore and Salesforce for enterprise data workflows (LiveAldar project).}
        \resumeItem{Built cross-platform mobile and web apps using React Native, Flutter, and Next.js with consistent UI/UX.}
        \resumeItem{Implemented geospatial map features with ArcGIS and multi-language support via Lokalise.}
        \resumeItem{Delivered across multiple client projects including DARI Value (React/Storybook), Fleetpartners (Drupal/CI/CD), and Smilebench (React/Auth0/Stripe).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Core Stack}{: TypeScript, React, Next.js, Node.js (NestJS / Express), PostgreSQL, AWS} \\
      \textbf{Frontend \& Mobile}{: JavaScript (ES6+), HTML5, CSS3, Redux, Angular, Vue.js, React Native, Flutter, Dart} \\
      \textbf{Backend \& Data}{: GraphQL, RESTful APIs, MongoDB, Elasticsearch, Redis, Python, Java} \\
      \textbf{Cloud \& DevOps}{: AWS (Cognito, EC2, S3), Azure, Docker, Kubernetes, CI/CD (Azure DevOps, Acquia), Git / GitHub / GitLab / Bitbucket} \\
      \textbf{Tools}{: Figma, Storybook, Postman, Jest, Mocha, Jira, Lokalise, ArcGIS, VS Code, Cursor} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Glocal University}{Uttar Pradesh, India}
      {B.Tech in Computer Science (Credit Transfer)}{Aug 2023 -- Jun 2025}
    \resumeSubheading
      {Kerala State Education Board}{Kerala, India}
      {Senior Secondary (Class XII)}{Jun 2013 -- Mar 2015}
    \resumeSubheading
      {Kerala State Education Board}{Kerala, India}
      {Secondary (Class X)}{Jun 2012 -- Mar 2013}
  \resumeSubHeadingListEnd

\end{document}